---
title: "08_Movies"
output: html_document
---

```{r}
# download data
# download.file("http://tiny.cc/dcf/MovieLens.rda", destfile = "MovieLens.rda")
# 
# library(dplyr)
# library(ggplot2)
# library(tidyr)
```

```{r}
# load data
load("MovieLens.rda")

# check for niceness
# three tables: Movies, Ratings, Users
head(Movies)
str(Movies)
```

# Task 1

Goal: Appeal of different genres to different sexes

## Method:

Data Sets:
-`Users` data table because that is where sex is stored. Variables:
  -`user_id`
  -`sex`
-`Movies` data table because that is where the genres are stored. Variables:
  -`movie_id`
  -genre columns
-Primary data will be ratings, from the Ratings table. Variables:
  -`rating`
  -`user_id`
  -`movie_id`

Visualization:
-Frame: x-axis is difference between average ratings per genre, y-axis is genre
-Glyph: Bar chart
-Statistics: Confidence interval

genre, difference between average ratings

```{r}
# consolidating the variables we need into a single table
CombinedRatings <- 
  Ratings %>% 
  select(-time_stamp) %>% 
  left_join(Users %>% select(user_id, sex), 
            by = "user_id") %>% 
  left_join(Movies %>% select(-movie_title, -release_date, -IMDb_URL), 
            by = "movie_id")
```


Now we gather the ratings into genre and sex and perform stats.
```{r}
# look at sex and genre as case
# then average rating (by sex and genre) and number of that sex who voted for that genre
# have head() to check results look reasonable as we go
GenreRatings <- 
  CombinedRatings %>% 
#  head(50) %>% 
  gather(genre, value, unknown:Western) %>% 
  filter(value) %>% 
  group_by(sex, genre) %>% 
  summarise(avgRating = mean(rating), numRatings = n(),
            stdError = sd(rating) / sqrt(n()))
```

Data is ready for plotting

```{r}
# plot some data!
# genre vs avgRating by sex
GenreRatings %>% 
  ggplot(aes(x = genre, y = avgRating, color = sex)) + #fill = sex when using bar
 # geom_bar(position = "dodge", stat = "identity") + #bc bars do nothing for us
  geom_point() +
  geom_line(aes(group = genre)) + # gives a visual for difference between sexes
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
# plot some data!
# genre vs number of votes by sex
GenreRatings %>% 
  ggplot(aes(x = genre, y = numRatings, fill = sex)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
# plot some data!
# genre vs number of votes by sex
GenreRatings %>% 
  select(-numRatings, -stdError) %>% 
  filter(genre != "unknown") %>% 
  spread(sex, avgRating) %>% # get rid of columns do NOT want to appear in output
  mutate(diff = M - F) %>% 
  ggplot(aes(x = reorder(genre, diff), y = diff, fill = sign(diff))) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Rating Different (M - F)") +
  guides(fill = FALSE)

  # also works
  # mutate(diff = M - F, sign = sign(diff)) %>% 
  # ggplot(aes(x = genre, y = diff, fill = sign) +
```







































